### 2025-07-01 index.qmd
20250701 - standardized regression coefficients

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "sn", "mclust", 
  "magrittr", "viridis", "plotly", "quantmod", "fPortfolio", "NMOF", "xts", #"webshot2",
  "zoo", "forecast", "stringi", "parallel", "parallelly", "doParallel", 
  "missRanger", "ggridges", "powerjoin", "caret", "gpboost", "cmdstanr", 
  "learnr", "remotes", "corrplot", "correlation", "mgcv", "rms", "car", 
  "performance", "lavaan", "mice", "miceadds", "interactions", "shiny", 
  "PearsonDS", "robustbase", "data.table", "future", "future.apply", "SimDesign"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", "mgcv", 
  "rms", "car", "performance", "lavaan", "mice", "miceadds", "interactions", 
  "shiny", "PearsonDS", "robustbase", "data.table", "future", "future.apply", 
  "QuantPsyc", "SimDesign", "effectsize"
)

### 2025-07-01 mixed-models.qmd
20250701 - standardized regression coefficients

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); cmdstanr::check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("broom.mixed")
library("tidybayes")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

summary(pointsPerSeason_nullModel)

@@

summary(pointsPerSeason_linearRegression)
summary(pointsPerSeason_linearRegression)$r.squared
AIC(pointsPerSeason_linearRegression)
MuMIn::AICc(pointsPerSeason_linearRegression)
```

@@

summary(pointsPerSeason_quadraticRegression)
summary(pointsPerSeason_quadraticRegression)$r.squared
AIC(pointsPerSeason_quadraticRegression)
MuMIn::AICc(pointsPerSeason_quadraticRegression)
```

@@

summary(pointsPerSeason_randomIntercepts)
MuMIn::r.squaredGLMM(pointsPerSeason_randomIntercepts)
performance::icc(pointsPerSeason_randomIntercepts)
AIC(pointsPerSeason_randomIntercepts)
AICc(pointsPerSeason_randomIntercepts)
```

@@

To obtain standardized regression coefficients, we use the `lm.beta.lmer()` function of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab].
We use the `emmeans` package [@R-emmeans] to determine the model-implied number of points per season by position.

@@

summary(pointsPerSeason_position)
petersenlab::lm.beta.lmer(pointsPerSeason_position)

@@

summary(pointsPerSeason_positionAgeFixedLinearSlopes)
petersenlab::lm.beta.lmer(pointsPerSeason_positionAgeFixedLinearSlopes)

@@

summary(pointsPerSeason_positionAgeRandomLinearSlopes)
petersenlab::lm.beta.lmer(pointsPerSeason_positionAgeFixedLinearSlopes)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)
petersenlab::lm.beta.lmer(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)
petersenlab::lm.beta.lmer(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
petersenlab::lm.beta.lmer(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)

>>>>

```{r}
library("lme4")
library("lmerTest")
library("effectsize")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); cmdstanr::check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("broom.mixed")
library("tidybayes")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

summary(pointsPerSeason_nullModel)
print(effectsize::standardize_parameters(pointsPerSeason_nullModel, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_linearRegression)
print(effectsize::standardize_parameters(pointsPerSeason_linearRegression, method = "refit"), digits = 2)

summary(pointsPerSeason_linearRegression)$r.squared
AIC(pointsPerSeason_linearRegression)
MuMIn::AICc(pointsPerSeason_linearRegression)
```

@@

summary(pointsPerSeason_quadraticRegression)
print(effectsize::standardize_parameters(pointsPerSeason_linearRegression, method = "refit"), digits = 2)

summary(pointsPerSeason_quadraticRegression)$r.squared
AIC(pointsPerSeason_quadraticRegression)
MuMIn::AICc(pointsPerSeason_quadraticRegression)
```

@@

summary(pointsPerSeason_randomIntercepts)
print(effectsize::standardize_parameters(pointsPerSeason_randomIntercepts, method = "refit"), digits = 2)

MuMIn::r.squaredGLMM(pointsPerSeason_randomIntercepts)
performance::icc(pointsPerSeason_randomIntercepts)
AIC(pointsPerSeason_randomIntercepts)
AICc(pointsPerSeason_randomIntercepts)
```

@@

To obtain standardized regression coefficients, we use the `standardize_parameters()` function of the `effectsize` package [@R-effectsize; @BenShachar2020_packages].
We use the `emmeans` package [@R-emmeans] to determine the model-implied number of points per season by position.

@@

summary(pointsPerSeason_position)
print(effectsize::standardize_parameters(pointsPerSeason_position, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_positionAgeFixedLinearSlopes)
print(effectsize::standardize_parameters(pointsPerSeason_positionAgeFixedLinearSlopes, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_positionAgeRandomLinearSlopes)
print(effectsize::standardize_parameters(pointsPerSeason_positionAgeRandomLinearSlopes, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes)
print(effectsize::standardize_parameters(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction)
print(effectsize::standardize_parameters(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction, method = "refit"), digits = 2)

@@

summary(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
print(effectsize::standardize_parameters(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience, method = "refit"), digits = 2)

### 2025-07-01 multiple-regression.qmd
20250701 - standardized regression coefficients

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("QuantPsyc")
library("broom")
library("tidyverse")
library("knitr")
```

@@

If we want to obtain standardized regression coefficients, we can use the `lm.beta()` function of the `QuantPsyc` package [R-QuantPsyc].

```{r}
QuantPsyc::lm.beta(linearRegressionModel)
```

@@

summary(linearRegressionModelStandardized)
```

@@

```{r}
QuantPsyc::lm.beta(quadraticTermsRegressionModel)
```

@@

summary(quadraticTermsRegressionModelStandardized)
```

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("broom")
library("tidyverse")
library("knitr")
```

@@

If we want to obtain standardized regression coefficients, we can use the `standardize_parameters()` function of the `effectsize` package [@R-effectsize; @BenShachar2020_packages].

```{r}
print(effectsize::standardize_parameters(linearRegressionModel, method = "basic"), digits = 2)
```

@@

summary(linearRegressionModelStandardized)

print(effectsize::standardize_parameters(linearRegressionModel, method = "refit"), digits = 2)
```

@@

```{r}
print(effectsize::standardize_parameters(quadraticTermsRegressionModel, method = "basic"), digits = 2)
```

@@

summary(quadraticTermsRegressionModelStandardized)

print(effectsize::standardize_parameters(quadraticTermsRegressionModel, method = "refit"), digits = 2)
```
